DOM bridges and barriers: systematic review and end-user survey

### 2025-09-20 reports/lit_codes_explore.qmd
res fig 2

## Code appearance frequencies across surveys (n = 21)

@@

  #calculate frequency of bridges vs. barriers being mentioned in surveys
code_freq_new_s <- codes_vars_s2 %>%
  mutate(br_pos = as.numeric(if_any(38:61, ~. == 1)), 
         ba_pos = as.numeric(if_any(21:37, ~. == 1)),
         br_reg = as.numeric(if_any(c(38:45), ~. ==1)),
         br_soc = as.numeric(if_any(c(46:55), ~. == 1)), 
         br_dat = as.numeric(if_any(c(56:57), ~. == 1)), 
         br_eco = as.numeric(if_any(c(58:61), ~. == 1)), 
         ba_reg = as.numeric(if_any(c(21:23), ~. == 1)),
         ba_dat = as.numeric(if_any(c(24:26), ~. == 1)), 
         ba_eco = as.numeric(if_any(c(27), ~. == 1)), 
         ba_soc = as.numeric(if_any(c(28:37), ~. == 1)))

brba_sum_s <- code_freq_new_s %>%
  summarise(n_br = sum(br_pos), freq_br = n_br/21,
            n_ba = sum(ba_pos), freq_ba = n_ba/21,
            n_br_e = sum(br_eco), freq_br_e = n_br_e/21,
            n_br_d = sum(br_dat), freq_br_d = n_br_d/21,
            n_br_s = sum(br_soc), freq_br_s = n_br_s/21,
            n_br_r = sum(br_reg), freq_br_r = n_br_r/21,
            n_ba_e = sum(ba_eco), freq_ba_e = n_ba_e/21,
            n_ba_d = sum(ba_dat), freq_ba_d = n_ba_d/21,
            n_ba_s = sum(ba_soc), freq_ba_s = n_ba_s/21, 
            n_ba_r = sum(ba_reg), freq_ba_r = n_ba_r/21) %>%  
  gather(br_ba, value, c(2,4,6, 8, 10, 12, 14, 16, 18, 20)) %>%
  subset(select = c(br_ba, value)) %>%
  mutate(percent_label = scales::percent(value, accuracy = 1), 
         percent = if_else(br_ba == "freq_ba" | br_ba == "freq_ba_e" | br_ba == "freq_ba_d" | br_ba == "freq_ba_s" | br_ba == "freq_ba_r", value, -value),
         code_level = if_else(br_ba %in% c("freq_ba", "freq_br"), "Overall bridge or barrier", 
                              if_else(br_ba %in% c("freq_ba_e", "freq_br_e"), "Ecological bridge or barrier", 
                              if_else(br_ba %in% c("freq_ba_d", "freq_br_d"), "Data bridge or barrier",
                              if_else(br_ba %in% c("freq_ba_r", "freq_br_r"), "Regulatory bridge or barrier",
                              if_else(br_ba %in% c("freq_ba_s", "freq_br_s"), "Social bridge or barrier", NA))))),
         code_brba = if_else(br_ba %in% c("freq_br", "freq_br_e", "freq_br_s", "freq_br_d", "freq_br_r"), "bridge", "barrier"),
         alpha_brba = if_else(br_ba %in% c("freq_br_e", "freq_br_s", "freq_br_d", "freq_br_r", "freq_ba_e", "freq_ba_s", "freq_ba_d", "freq_ba_r"), "alpha", "no_alpha")) %>%
  group_by(code_level)

brba_sum_s$code_level <- factor(brba_sum_s$code_level, levels = c("Ecological bridge or barrier", "Data bridge or barrier", "Regulatory bridge or barrier","Social bridge or barrier", "Overall bridge or barrier"))
brba_sum_s$code_brba <- factor(brba_sum_s$code_brba, levels = c("bridge", "barrier"))

@@

#### Regulatory frequencies

@@

code_sum_s <- code_freq_s %>%
  group_by(bridge_barr) %>%
  mutate(n_total = sum(total)) %>%
  ungroup() %>%
  group_by(code_cat) %>% 
  mutate(n_subtotal = sum(total)) %>%
  summarise(value = n_subtotal/n_total) %>%
  rename("br_ba" = code_cat) %>%
  mutate(percent_label = scales::percent(value, accuracy = 1), 
         percent = if_else(br_ba == "Data barrier" | br_ba == "Ecological barrier" | br_ba == "Social barrier" | br_ba == "Regulation barrier", value, -value),
         code_level = if_else(br_ba %in% c("Ecological barrier", "Ecological bridge"), "Ecological bridge or barrier", 
                              if_else(br_ba %in% c("Data barrier", "Data bridge"), "Data bridge or barrier",
                              if_else(br_ba %in% c("Regulation barrier", "Regulation bridge"), "Regulatory bridge or barrier",
                              if_else(br_ba %in% c("Social barrier", "Social bridge"), "Social bridge or barrier", NA)))), 
         code_brba = if_else(br_ba %in% c("Data bridge", "Ecological bridge", "Social bridge", "Regulation bridge"), "bridge", "barrier")) %>%
  group_by(code_level) %>%
  distinct()

code_sum_s$code_level <- factor(code_sum_s$code_level, levels = c("Ecological bridge or barrier", "Data bridge or barrier","Regulatory bridge or barrier", "Social bridge or barrier"))
code_sum_s$code_brba <- factor(code_sum_s$code_brba, levels = c("bridge", "barrier"))

@@

#### Regulatory codes
:::

>>>>

## Code appearance frequencies across surveys (n = 2, not including EcoCast)

@@

  #calculate frequency of bridges vs. barriers being mentioned in surveys
code_freq_new_s <- codes_vars_s2 %>%
  mutate(br_pos = as.numeric(if_any(37:54, ~. == 1)), 
         ba_pos = as.numeric(if_any(21:36, ~. == 1)),
         br_reg = as.numeric(if_any(c(37:44, 50), ~. ==1)),
         br_soc = as.numeric(if_any(c(45:49, 51), ~. == 1)), 
         br_dat = as.numeric(if_any(c(52), ~. == 1)), 
         br_eco = as.numeric(if_any(c(53, 54), ~. == 1)), 
         ba_reg = as.numeric(if_any(c(21, 22), ~. == 1)),
         ba_dat = as.numeric(if_any(c(23:25), ~. == 1)), 
         ba_eco = as.numeric(if_any(c(26), ~. == 1)), 
         ba_soc = as.numeric(if_any(c(27:36), ~. == 1)))

brba_sum_s <- code_freq_new_s %>%
  summarise(n_br = sum(br_pos), freq_br = n_br/21, #total number of surveys not including EcoCast
            n_ba = sum(ba_pos), freq_ba = n_ba/21,
            n_br_e = sum(br_eco), freq_br_e = n_br_e/21,
            n_br_d = sum(br_dat), freq_br_d = n_br_d/21,
            n_br_s = sum(br_soc), freq_br_s = n_br_s/21,
            n_br_r = sum(br_reg), freq_br_r = n_br_r/21,
            n_ba_e = sum(ba_eco), freq_ba_e = n_ba_e/21,
            n_ba_d = sum(ba_dat), freq_ba_d = n_ba_d/21,
            n_ba_s = sum(ba_soc), freq_ba_s = n_ba_s/21, 
            n_ba_r = sum(ba_reg), freq_ba_r = n_ba_r/21) %>%  
  gather(br_ba, value, c(2,4,6, 8, 10, 12, 14, 16, 18, 20)) %>%
  subset(select = c(br_ba, value)) %>%
  mutate(percent_label = scales::percent(value, accuracy = 1), 
         percent = if_else(br_ba == "freq_ba" | br_ba == "freq_ba_e" | br_ba == "freq_ba_d" | br_ba == "freq_ba_s" | br_ba == "freq_ba_r", value, -value),
         code_level = if_else(br_ba %in% c("freq_ba", "freq_br"), "Overall bridge or barrier", 
                              if_else(br_ba %in% c("freq_ba_e", "freq_br_e"), "Ecological bridge or barrier", 
                              if_else(br_ba %in% c("freq_ba_d", "freq_br_d"), "Data bridge or barrier",
                              if_else(br_ba %in% c("freq_ba_r", "freq_br_r"), "Implementation bridge or barrier",
                              if_else(br_ba %in% c("freq_ba_s", "freq_br_s"), "Social bridge or barrier", NA))))),
         code_brba = if_else(br_ba %in% c("freq_br", "freq_br_e", "freq_br_s", "freq_br_d", "freq_br_r"), "bridge", "barrier"),
         alpha_brba = if_else(br_ba %in% c("freq_br_e", "freq_br_s", "freq_br_d", "freq_br_r", "freq_ba_e", "freq_ba_s", "freq_ba_d", "freq_ba_r"), "alpha", "no_alpha")) %>%
  group_by(code_level)

brba_sum_s$code_level <- factor(brba_sum_s$code_level, levels = c("Ecological bridge or barrier", "Data bridge or barrier", "Implementation bridge or barrier","Social bridge or barrier", "Overall bridge or barrier"))
brba_sum_s$code_brba <- factor(brba_sum_s$code_brba, levels = c("bridge", "barrier"))

@@

#### Implementation frequencies

@@

code_sum_s <- code_freq_s %>%
  group_by(bridge_barr) %>%
  mutate(n_total = sum(total)) %>%
  ungroup() %>%
  group_by(code_cat) %>% 
  mutate(n_subtotal = sum(total)) %>%
  summarise(value = n_subtotal/n_total) %>%
  rename("br_ba" = code_cat) %>%
  mutate(percent_label = scales::percent(value, accuracy = 1), 
         percent = if_else(br_ba == "Data barrier" | br_ba == "Ecological barrier" | br_ba == "Social barrier" | br_ba == "Regulation barrier", value, -value),
         code_level = if_else(br_ba %in% c("Ecological barrier", "Ecological bridge"), "Ecological bridge or barrier", 
                              if_else(br_ba %in% c("Data barrier", "Data bridge"), "Data bridge or barrier",
                              if_else(br_ba %in% c("Regulation barrier", "Regulation bridge"), "Implementation bridge or barrier",
                              if_else(br_ba %in% c("Social barrier", "Social bridge"), "Social bridge or barrier", NA)))), 
         code_brba = if_else(br_ba %in% c("Data bridge", "Ecological bridge", "Social bridge", "Regulation bridge"), "bridge", "barrier")) %>%
  group_by(code_level) %>%
  distinct()

code_sum_s$code_level <- factor(code_sum_s$code_level, levels = c("Ecological bridge or barrier", "Data bridge or barrier","Implementation bridge or barrier", "Social bridge or barrier"))
code_sum_s$code_brba <- factor(code_sum_s$code_brba, levels = c("bridge", "barrier"))

@@

#### Implementation codes
:::
